Towards Cloud Bursting for Extreme Scale Supercomputers

### 2014-06-12 paper/paper.tex
0611

\subsection{data reading}
When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splited into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assgined a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.

>>>>

\subsection{data reading}

\begin{figure}[tb]
	\centering
	\includegraphics[width=8cm]{reading}
	\caption{data reading operation}
	\label{reading}
\end{figure}

When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splited into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assgined a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.
